---
name: Derek McCrae Norton
address: "7315 Ashley Trace, Cumming, GA 30028"
phone: (404) 805-7927
email: "dnorton1@gmail.com"
twitter: dermcnor
github: dermcnor
linkedin: dermcnor
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output: 
  vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(readr)
library(dplyr)
library(tidyr)
```

# Introduction

\footnotesize
Director level analytics leader that is well versed in advanced statistical methods, predictive modeling, machine learning with specific focus on marketing analytics, credit scoring, and healthcare analytics.

Proven ability to:

* Build and manage analytics teams.
* Develop, implement, and support complex statistical modeling, analysis and reporting techniques.
* Consult and educate clients on enterprise analytics.
* Develop and conduct analytic training.

Specialties: Analytic Leadership, Analytic Consulting, Predictive Analytics, Data Science, Machine Learning 


# Employment

```{r}
read_csv("work-history.csv") %>%
  mutate(dates = paste(from, to, sep = " - ")) %>% 
  detailed_entries(what = position, 
                   when = dates,
                   with = company, 
                   where = location,
                   why = details)
```

# Education

\footnotesize
```{r education, results='asis'}
read_csv("education.csv") %>%
  mutate(degree = paste0("\\textbf{", degree, "}")) %>% 
  unite("edu", degree:dates, sep = ", ") %>% 
  pull(edu) %>% 
  cat(sep = "\n\n")
```

```{r}
read_csv("education.csv") %>%
  detailed_entries(.protect = TRUE,
    what = university,
    when = dates,
    with = degree,
    where = location
  )
```


# Select Conference Presentations

```{r}
read_csv("presentations.csv") %>%
  brief_entries(what = glue::glue("\\textbf{<title>} \\newline <conference>, <location> \\newline <url>", 
                                  .open = "<", .close = ">"), 
                when = date, 
                .protect = FALSE)
```

# TECHNICAL SKILLS

\footnotesize
* __Statistics__: Predictive Modeling, Capture-Recapture Methods, Time Series Analysis, Text Mining
* __Programming__: R, SQL, SAS, Python
* __Big Data__: Hadoop, Spark


# OTHER ACCOMPLISHMENTS

\footnotesize
* Founder and Director of the Atlanta R User Group (2008 – Present).
* Over 500 hours tutoring and teaching advanced statistics.

